%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\customresumeItem}[1]{
  \item\small{
    #1
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\customresumeSubheading}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3} \\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeSubSubheading}[1]{
    \vspace{0.05pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[itemsep=0.01pt, leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize} \vspace{-8pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=0.01pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}  \vspace{-8pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/satish0208/}{\Large Karri Sai Satish Kumar Reddy}} & Email : \href{mailto:ksskreddy2015@gmail.com}{ksskreddy2015@gmail.com}\\
  Mobile : +919932028385 & LinkedIn : \href{https://www.linkedin.com/in/satish0208/}{satish0208} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology Kharagpur}{Kharagpur, India}
      {Bachelor Of Technology in Computer Science And Engineering; CGPA: 9.08/10}{July 2015 -- July 2019}
  \resumeSubHeadingListEnd
  \vspace{5pt}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
{Google}{Bangalore, India}
{Software Engineer III}{August 2021 - Present}
\resumeItemListStart
\customresumeItem
{Led (\href{https://ec.europa.eu/commission/presscorner/detail/en/ip_24_1689}{DMA Complaince}) efforts across 15 pipelines, coordinating with partner teams and spearheading data labeling initiatives for DMA compliance. Worked closely with legal counsel to ensure alignment with regulatory requirements. }
\customresumeItem
{Owned brand entity ingestion and serving pipeline, successfully launching Brand Exclusions in PMax, supporting \textbf{200K+ customers and 900M+ Weekly ARR.}}
\customresumeItem
{Played a key role in launching the Commercial Knowledge Graph infrastructure by designing critical components like the proto triplification library and file-based locking system.}
\customresumeItem
{Established processes within the team to ensure (\href{https://cloud.google.com/learn/what-is-data-governance}{Data Governance}) compliance for all launches. Collaborated with Privacy counsel to resolve potential violations and develop contingency plans.}
\resumeItemListEnd

    \resumeSubheading
      {Cohesity}{Bangalore, India}
      {Research Engineer}{July 2019 - August 2021}
         \resumeItemListStart
            \customresumeItem
            {Designed and developed object based backups, which is a key feature of \textbf{DMaaS (Data Management as a Service)}.}
            \customresumeItem
            {Delivered \textbf{performance/scale improvements} in the control path operations for performing backups/restores.}
            \customresumeItem
             {Redesigned and massively parallelized operations of the Pulse service, resolving UI scalability issues and achieving a remarkable \textbf{60\% performance boost.}}
        \resumeItemListEnd
         
        

    \resumeSubheading
      {Intuit}{Bangalore, India}
      {Software Engineering Intern}{May 2018 - July 2018}
        \resumeSubSubheading
        {\textbf{Aurora Adapter}}
        \resumeItemListStart
            \customresumeItem
             {Designed and developed a \textbf{fault tolerant, highly available} module called Aurora Adapter}\
             \customresumeItem
             {This \textbf{ETL module} is pivotal in extracting data from Aurora MySQL database instances utilizing Debezium, a Kafka Connect-based platform. It further transforms and ingests data into the Data Lake infrastructure.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd
  \vspace{5pt}


%-----------PROJECTS-----------------

\section{Academic Projects}
\resumeSubHeadingListStart

\customresumeSubheading
{Memory Resident Unix-like File-System}{March 2018}
{Operating Systems Lab}
\resumeItemListStart
\customresumeItem
{Implemented a memory resident \textbf{Unix-Like file system} (MRFS) with support for multiple users via a C library of APIs.Developed APIs encompassing standard Unix file operations and full system state saving and restoration.}
\resumeItemListEnd
\vspace{5pt}

\customresumeSubheading
{Transport Wrapper}{March 2018}
{Networks Lab}
\resumeItemListStart
\customresumeItem
{Created a modular \textbf{Transport layer wrapper} atop UDP protocol for reliable data transfer using socket programming. Implemented flow control and congestion control mechanisms.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{5pt}
  
%--------ACHIEVEMENTS------------------

\section{Achievements}

   \resumeItemListStart
   \customresumeItem
   {Received the prestigious \textbf{CHAIRMAN BOARD OF GOVERNORS GOLD MEDAL} on 65th convocation of IIT Kharagpur for being best all-rounder performer under disabled category.}
   \customresumeItem
   {Nominated as the best performer and received Top Gun Manverick Award for a quarter in Cohesity.}
   \customresumeItem
   {Stood \textbf{52nd} in \textbf{ACM-ICPC(2018) Online Qualifiers} and qualified for the Amritapuri Regionals}
   \customresumeItem
   {Ranked \textbf{83rd} in the \textbf{Amritapuri onsite regionals} of ACM ICPC 2018.}
   \customresumeItem
   {Secured \textbf{8th} Rank in \textbf{JEE ADVANCED 2015} in OC-PH category.}
   \resumeItemListEnd
%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item[]{
     \textbf{Languages}{: Fluent in C, C++, Experienced in Golang, Python, Java.} \\
     \textbf{Tools/Libraries}{: Experienced in Protocol Buffers, Git, AWS, Docker, Kafka, Confluent, React}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
