%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS 
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style 
\usepackage{hyperref} 
\usepackage[left=0.4 in,top=0.3 in,right=0.4 in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{KARRI SAI SATISH KUMAR REDDY} % Your name 
\address{COMPUTER SCIENCE AND ENGINEERING \\ BTECH 4Y} % Your address 
%\address{123 Pleasant Lane  City, State 12345} % Your secondary addess (optional) 
\address{+91 9932028385 \\ ksskreddy2015@gmail.com} % Your phone number and email

\begin{document}  

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor Of Technology In Computer Science And Engg} \hfill {July 2015 - present}
\\ 
Indian Institute of Technology,Kharagpur, CGPA: 9.08/10.00   

{\bf Intermediate Education, Class XII} \hfill {June 2013 - April 2015}
\\ 
Narayana Junior College,Andhra Pradesh, 97.4\%

{\textbf{SSC, Class X}}  \hfill{March 2012 - March 2013}\\
Pragathi Little Public School,Andhra Pradesh, 9.7/10.0    
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection} 

%-----------------------------------------------------------------------------
 % WORK EXPERIENCES
 %-----------------------------------------------------------------------------
  
\begin{rSection}{WORK EXPERIENCES}

\begin{rSubsection}{Software Engineering Intern , Intuit }{May 2018 - July 2018}{\textbf{Aurora Adaptor}}{}              
\item Involved in design and development of a module called adaptor which consumes data from Aurora mysql database instances using
Debezium,a kafka connect based platform.
\item The designed Adaptor was fault tolerant,highly available and can be used for any mysql database. 
\item Used SMT to convert  the consumed data to required schema and pushed to kafka in real time.
\end{rSubsection}  

%------------------------------------------------
\end{rSection}


%--------------------------------------------------------------------------------------
%  COMPETITIONS
%--------------------------------------------------------------------------------------
\begin{rSection}{ PROGRAMMING ACHEIVEMENTS } \itemsep -3pt        

\item Stood \textbf{52nd} in \textbf{ACM-ICPC(2018) Online Qualifiers} and qualified for the Amritapuri Regionals 
\item Ranked \textbf{83rd} in the \textbf{Amritapuri onsite regionals} of ACM ICPC 2018.
\item Runner-up in the event \textbf{SourceCode}, held in Kshitij 2018, IIT Kharagpur
\item Bagged 3rd position in \textbf{CodersBit} conducted by InterviewBit among all students of IIT Kharagpur
\item Stood 81st in \textbf{CodersBit Finale} conducted by InterviewBit among the top 1200 finalists.
\item Qualified for the \textbf{SnackDown 2017 Online Elimination Round}(pre-final)  by competing with 3300 teams
 
\end{rSection}


\begin{rSection}{ ACADEMIC ACHEIVEMENTS } \itemsep -3pt        

\item Secured 8th Rank in JEE ADVANCED 2015 in OC-PH category.
\item Secured 1st Rank in JEE MAINS(B.Tech) 2015 in OC-PH category with a percentile of 99.33.
\item Secured a rank of 662 in APEAMCET 2015 in General Category. 
\end{rSection}





%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS AND EXPERTISE}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }  
Languages &  Fluent in C, C++ :  Experienced in Python,Java\\    
Tools/Libraries & Experienced in TensorFlow, Git, NumPy, Pandas, MySQL, AWS, Docker,\\& Kafka, Confluent, Android Studio, Django \\      
 
\end{tabular}   

\end{rSection}

  

%-------------------------------------------------------------------------------
%	PROJECTS

\begin{rSection}{ACADEMIC PROJECTS}

% \begin{rSubsection}{Hospital Management System} {March 2017}{\textbf{Software Engineering Lab}}{}

% \item Developed a software in java using Swing Package which can be used by Doctors, Patients and Receiptionist.
% \item Functionalities include  registration-login module for every user, generate the medical bills, assign doctors to patients,write report to the patients,view the Doctor's Report and Bills paid.
% \end{rSubsection}  

%------------------------------------------------

\begin{rSubsection}{Memory Resident Unix like File-System } {March 2018}{\textbf{Operating Systems Lab}}{}

\item Implemented a memory resident Unix-Like file system (MRFS) supporting multiple users that can be accessed using a library of APIs in C.
\item The APIs include all the standard unix file operations,copying files between the file system and PC file system and dumping it to PC file system and restoring from it etc.
\end{rSubsection}  

\begin{rSubsection}{Transport Wrapper} {March 2018}{\textbf{Networks Lab}}{}

\item Implemented an modular Transport layer wrapper on top of unreliable UDP protocol for reliable data
transfer using socket programming.
\item Implemented flow control, congestion control following various optimizations like slow start, fast recovery,\\fast retransmission over UDP services.
\end{rSubsection}  


\begin{rSubsection}{Motion Clustering} {March 2018 - Present }{\textbf{Bachelor Thesis}}{}

\item Implemented a model to cluster similar motion frames in a dance video and obtained an accuracy of 80\%.
\item Used \textbf{Dynamic Time Warping}(DTW) for measuring similarity between two motion frames and \textbf{Spectral Clustering} for clustering them.
\end{rSubsection}  


\begin{rSubsection}{Amazon Outlivers} {Sep 2017 - Nov 2017}{\textbf{Intelligent Game Design}}{}

\item Developed a 3D survival game with Unity using various AI techniques to generate intelligent behaviors in \\non-player characters (animals).
\item Implemented path planning using A-star,priority based blending of steering behaviours,movement algorithms like seek,flee,wander etc and collision avoidance using ray casting.
\end{rSubsection}  


%-------------------------------------------------


\begin{rSubsection}{Ray Tracing on triangle meshes} {March 2018 - April 2018}{\textbf{Computer Graphics }}{}

\item Generated an animated GIF by using ray tracing on the objects in the scene while rotating them smoothly.
\item Implemented Ambient,Spherical,Diffuse Illuminations along with shadows for realistic effect.
\end{rSubsection}  


%-------------------------------------------------- 




\end{rSection} 



\begin{rSection}{OTHER PROJECTS}

\begin{rSubsection}{FightForge , Smart India Hackathon} {March 2019}{Fake currency notes detector}{}
\item Developed an android app which uses Image Processing to detect whether the note was fake or real which bagged first prize at Smart India hackathon.           
\item The user can upload the currency note pic and the app would verify its authenticity using 25 features extracted from front and rear side of the currency note.
\end{rSubsection}

\end{rSection}







%	COURSEWORK INFORMATION 
%----------------------------------------------------------------------------------------

\begin{rSection}{COURSEWORK INFORMATION} \itemsep -3pt  

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }  
Completed &  Algorithms*, Software Engineering*, Operating Systems*, Computer Graphics*, \\& Computer Networks*,Machine Learning,Intelligent Game Design, Compilers*,\\& Computer Organisation and Architecture*, Discrete Structures,Parallel Algorithms,\\& Cryptography\\
Ongoing & Distributed Systems, Cloud Computing, Educational Data Analytics.\\
Online & Machine Learning (Coursera), App Development(Udacity).
 
\end{tabular}   

* marked courses had a laboratory component as well

\end{rSection}  
 
 

%--------------------------------------------------------------------------------------
% Extra-Cirrucular
%--------------------------------------------------------------------------------------

\begin{rSection}{Links/Handle} \itemsep -2pt   
\item Codechef : \href{https://www.codechef.com/users/ksskreddy2015}{ksskreddy2015}
\item Hackerrank : \href{https://www.hackerrank.com/Namakian}{Namakian}
\item Linkedin : \href{https://www.linkedin.com/in/karri-sai-satish-kumar-reddy-5548b1117/}{Satish}

\item Github :\href{https://github.com/ksskreddy}{ksskreddy}


\end{rSection} 

  

\end{document}
