%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage[T1]{fontenc}
\newcommand\mybar{\kern1pt\rule[-\dp\strutbox]{.8pt}{\baselineskip}\kern1pt}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{0pt}}
  }
}

\newcommand{\customresumeItem}[1]{
  \item\small{
    #1
  }
}

\newcommand{\myresumeSubItem}[3]{
\item\small{
    \textbf{#1}, \textit{\small #2}{: #3 \vspace{-6pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\customresumeSubheading}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3} \\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeSubSubheading}[1]{
    \vspace{0.05pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[itemsep=0.01pt, leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize} \vspace{-8pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=0.01pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}  \vspace{-8pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/satish0208/}{\Large Karri Sai Satish Kumar Reddy}} & Email : \href{mailto:ksskreddy2015@gmail.com}{ksskreddy2015@gmail.com}\\
  Mobile : +91-9932028385 & LinkedIn : \href{https://www.linkedin.com/in/satish0208/}{satish0208} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology Kharagpur}{Kharagpur, India}
      {Bachelor Of Technology in Computer Science And Engineering; CGPA: 9.08/10}{July 2015 -- July 2019}
  \resumeSubHeadingListEnd
  \vspace{5pt}


%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Cohesity}{Bangalore, India}
      {Research Engineer}{July 2019 - Present}
         \resumeSubSubheading{\textbf{Object Based Backups (DMaaS)}}
             \resumeItemListStart
             \customresumeItem
             {Involved in design and development of object based backups which is the prime feature in the initial offering of \textbf{DMaaS(Data Management as a Service)}.}
            \customresumeItem
             {As part of Magneto-Infra team, involved in delivering various performance/scale improvements in the control path operations for performing the backups/restores.}
             \customresumeItem
             {Currently working on the project \textbf{DRaaS(Disaster Recovery as a Service)} which is one of the next biggest upcoming feature.}
             \resumeItemListEnd
      
        \resumeSubSubheading{\textbf{Pulse}}
             \resumeItemListStart
             \customresumeItem
             {Involved in redesigning of a service called Pulse(Progress monitoring service) which used to cause various scale issues like UI slowness and stalling of backups in large deployments.}
             \customresumeItem
             {Massively parallelized the operations of pulse by implementing fine grained locking, flow control, client/server side batching, caching which resulted in improving the overall service performance by 60\%.}
             \resumeItemListEnd
        \vspace{5pt}
        

    \resumeSubheading
      {Intuit}{Bangalore, India}
      {Software Engineering Intern}{May 2018 - July 2018}
        \resumeSubSubheading
        {\textbf{Aurora Adapter}}
        \resumeItemListStart
            \customresumeItem
             {Involved in design and development of a module called adaptor which consumes data from Aurora mysql database instances using Debezium,a kafka connect based platform.}
             \customresumeItem
             {The designed Adaptor was fault tolerant,highly available and can be used for any mysql database.}
             \customresumeItem
             {Used SMT to convert the consumed data to required schema and pushed to kafka in real time.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd
  \vspace{5pt}


%-----------PROJECTS-----------------
\section{Academic Projects}
  \resumeItemListStart
   
   \resumeItem{Motion Clustering}{\textit{Bachelors Thesis }Clustering of similar motions in the given Bharatanatyam dance video. Achieved an accuracy of 80\% by using DTW as similarity measure and spectral clustering. \href{https://github.com/ksskreddy/BTP}{\hspace{0.5ex}\faGithub}}
    \resumeItem{Flamingo}
      {Distributed cluster middleware system for job submission and monitoring.It performs Job scheduling, starvation free match-making, job premption and migration.\href{https://github.com/ranjithkumar007/flamingo}{\hspace{0.5ex}\faGithub}}
    \resumeItem{TransWrapper}
      {Google QUIC like modular transport layer wrapper on top of UDP.Implemented 
flow control, congestion control following optimizations like slow start, fast recovery etc over the UDP protocol.}
      \resumeItem{File System}{Implemented a memory resident Unix-Like file system (MRFS) supporting multiple users which provides all the standard linux file operations. \href{https://github.com/Suriya17/MRFS}{\hspace{0.5ex}\faGithub}}

  \resumeItemListEnd
  \vspace{5pt}
  
%--------ACHIEVEMENTS------------------

\section{Achievements}

   \resumeItemListStart
   \customresumeItem
   {Nominated as the best performer and received Top Gun Manverick Award for a quarter in Cohesity.}
   \customresumeItem
   {Received the prestigious \textbf{CHAIRMAN BOARD OF GOVERNORS GOLD MEDAL} on 65th convocation of IIT Kharagpur for being best all-rounder performer under disabled category.}
   \customresumeItem
   {Stood \textbf{52nd} in \textbf{ACM-ICPC(2018) Online Qualifiers} and qualified for the Amritapuri Regionals}
   \customresumeItem
   {Ranked \textbf{83rd} in the \textbf{Amritapuri onsite regionals} of ACM ICPC 2018.}
   \customresumeItem
   {Secured \textbf{8th} Rank in \textbf{JEE ADVANCED 2015} in OC-PH category.}
   \resumeItemListEnd
%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item[]{
     \textbf{Languages}{: Fluent in C, CPP, Experienced in Golang, Python, Java.} \\
     \textbf{Tools/Libraries}{: Experienced in Protocol Buffers, Git, AWS, Docker, Kafka, Confluent}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
